How to select predictive models for decision-making or causal inference?

### 2023-12-17 how_to_select_causal_models.tex
iter

We also use three semi-simulated
data adding a known synthetic causal effect to real --non synthetic-- healthcare
covariate. ACIC 2016 \cite{dorie_automated_2019} is based on the Collaborative
Perinatal Project \cite{niswander_women_1972}, a RCT studying infants’
developmental disorders containing 4,802 indivduals and 55 features. We used 770
dataset instances: 10 random seeds for each of the 77 simulated settings for the
treatment and outcomes.  ACIC 2018 \cite{shimoni_benchmarking_2018} simulated
treatment and outcomes for the Linked Births and Infant Deaths Database (LBIDD)
\cite{macdorman_infant_1998} with $D=177$ covariates. We used all 432 datasets
of size $N=5\,000$.  Twins \cite{louizos_causal_2017} is an augmentation of real
data on twin births and mortality rates \cite{almond_costs_2005}. There are
$N=11\,984$ samples, and $D=50$ covariates for which we simulated 1,000
different treatment allocations. Datasets details are given in Appendix
\ref{apd:experiments:datasets}.

@@

Drawing inspiration from the TMLE literature that uses combination of flexible
machine learning methods \cite{schuler_targeted_2017}, we model the nuisances
$\check e$ (respectivley $\check m$) with a meta-learner: a stacked estimator of ridge
and boosting classifiers (respectively regressions) (hyperparameter selection in Appendix \ref{apd:experiments:nuisances_hp}).

>>>>

We also use three semi-simulated
data adding a known synthetic causal effect to real --non synthetic-- healthcare
covariate. ACIC 2016 \cite{dorie_automated_2019} is based on the Collaborative
Perinatal Project \cite{niswander_women_1972}, a RCT studying infants’
developmental disorders containing 4,802 indivduals and 55 features. We used 770
dataset instances: 10 random seeds for each of the 77 simulated settings for the
treatment and outcomes.  ACIC 2018 \cite{shimoni_benchmarking_2018} simulated
treatment and outcomes for the Linked Births and Infant Deaths Database (LBIDD)
\cite{macdorman_infant_1998} with $D=177$ covariates. We used all 432 datasets
of size $N=5\,000$.  Twins \cite{louizos_causal_2017} is an augmentation of real
data on twin births and mortality rates \cite{almond_costs_2005}. There are
$N=11\,984$ samples, and $D=50$ covariates for which we simulated 1,000
different treatment allocations. Appendix
\ref{apd:experiments:datasets} gives datasets details.

@@

Drawing from the TMLE literature that uses combination of flexible
machine learning methods \cite{schuler_targeted_2017}, we model the nuisances
$\check e$ (respectivley $\check m$) with a meta-learner: a stacked estimator of ridge
and boosting classifiers (respectively regressions) (hyperparameter selection in Appendix \ref{apd:experiments:nuisances_hp}).
